---
title: "Summarize Simulation Results"
author: "Gabriel J. Odom, PhD, ThD"
date: "July 12, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Overview
This document will walk through reading in all the simulation results in a given directory, and summarizing and saving these results. This script requires a directory replete with the simulation results obtained by executing the `WriteDMRcateResults()`, `WriteProbeLassoResults()`, or `WriteBumphunterResults()` functions. For the Comb-p method, simulation execution should be performed via the `Python` programming language, because there does not yet exist an `R` package for this method. Once you have completed your simulation work and have saved all the raw data files as compressed `.RData`, `.RDS`, or `.rda` files (we use `.RDS`), then you can run the code below to import and summarize these data files.



# Process Raw Results
We first load the necessary packages and master data sets. The master data sets are the data files used to generate the simulated data, i.e., the truth or gold standard results. We need these data files to measure each method's performance. The `betVals_mat` is a matrix of $\beta$ values, and `startEndCPG_df` is a data frame of `Aclust` clustering results. You should change the `resultsDir` string to reflect where your results are stored.
```{r packages_and_data}
library(DMRcompare)
library(tidyverse)
data("betaVals_mat")
data("startEndCPG_df")
resDir <- "~/Documents/GitHub/DMRcomparison_results/"
```


## DMRcate Results
This takes roughly 4.5 minutes on my machine.
```{r DMRcate_res}
a <- Sys.time()
dmrcateRes_df <- ProcessDMRcateResults(resultsDir = resDir,
                                       beta_mat = betaVals_mat,
                                       AclustCPG_df = startEndCPG_df)
Sys.time() - a
```

Save the summary to the data directory. If you'd like the summaries in a different location, you can change the path in the call to the `dir.create` function as stored in the `summaryDir` string.
```{r save_DMRcate}
summaryDir <- paste0(resDir, "Summaries/")
dir.create(summaryDir)
write_csv(
  dmrcateRes_df,
  path = paste0(summaryDir, "DMRcate_results.csv")
)
```


## ProbeLasso Results
This takes roughly 9 minutes on my machine.
```{r PL_res}
a <- Sys.time()
probeLassoRes_df <- ProcessProbeLassoResults(resultsDir = resDir,
                                             beta_mat = betaVals_mat,
                                             AclustCPG_df = startEndCPG_df)
Sys.time() - a
```

Save the summary.
```{r save_PL}
write_csv(
  probeLassoRes_df,
  path = paste0(summaryDir, "ProbeLasso_results.csv")
)
```


## Bumphunter Results
This takes roughly 3 minutes on my machine.
```{r Bump_res}
a <- Sys.time()
bumphunterRes_df <- ProcessBumphunterResults(resultsDir = resDir,
                                             beta_mat = betaVals_mat,
                                             AclustCPG_df = startEndCPG_df)
Sys.time() - a
```

Save the summary.
```{r save_Bump}
write_csv(
  bumphunterRes_df,
  path = paste0(summaryDir, "Bumphunter_results.csv")
)
```


## Comb-p Results
These results will be require a different setup. Because these results were not calculated in `R` with the other method results, we also need the CPG locations data set. This takes roughly 8 minutes on my machine.
```{r Combp_res}
data("cpgLocation_df")

a <- Sys.time()
combpRes_df <- ProcessCombpResults(resultsDir = resDir,
                                   beta_mat = betaVals_mat,
                                   AclustCPG_df = startEndCPG_df,
                                   cpgLocation_df = cpgLocation_df)
Sys.time() - a
```

Save the summary.
```{r save_Combp}
write_csv(
  combpRes_df,
  path = paste0(summaryDir, "Comb-p_results.csv")
)
```
